%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Siva}{Nandipati}{ \urlstyle{same}\href{http://sivachow.github.io}{sivachow.github.io}| 
\href{mailto:NandipatiSivaChowdeswar@gmail.com}{NandipatiSivaChowdeswar@gmail.com} | 587.778.4534 | \href{mailto:dd367@cornell.edu}{dd367@cornell.edu}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Alberta}
\descript{Bachlor of Science \\ Departmental Honors in Computer Science}
\location{Edmonton, AB}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/Sivachow}{\bf deedydas} \\
LinkedIn://  \href{https://www.linkedin.com/in/debarghyadas}{\bf debarghyadas} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Computer Science}
Advanced Data Structures \\
Design \& Analysis of Algorithms\\
Machine Learning\\
Reinforcement Learning\\
Functional \& Scripting Languages\\
Computer Systems\\
Object Oriented Programming\\
Open Source Software Engineering \\
Compilers + Practicum \\
Operating Systems \\
Artificial Intelligence + Practicum \\
Functional Programming \\
Computer Graphics + Practicum \\
\sectionsep

\subsection{Mathematics/Statistics}
Probability Theory\\
Applications of Linear Algebra\\
Mathematics of Finance\\
Computational Methods\\
Applied Probability and Statistics\\
Multivariate Calculus\\
Differential Equations\\
Unix Tools and Scripting \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 5000 lines:}
Java \textbullet{}   Shell \textbullet{} Python \textbullet{} Javascript \\
OCaml \textbullet{} Matlab \textbullet{} Rails \textbullet{} \LaTeX\ \\ 
\location{Over 1000 lines:}
C \textbullet{} C++ \textbullet{} CSS \textbullet{} PHP \textbullet{} Assembly \\
\location{Familiar:}
AS3 \textbullet{} iOS \textbullet{} Android \textbullet{} MySQL
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{MNP Digital}
\descript{| Software Developer Intern }
\location{May 2022 - Aug 2022 | Edmonton, AB\\ MNP Rewrite Project}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Led the rewriting of MNP Canada Digital Adoption Program's API, converting it into in-house Spring Boot microservices using Java, resulting in a 40\% increase in service availability.
\item Collaborated with a cross-functional team of 15 developers and architects to seamlessly integrate microservices, resulting in a 30\% reduction in defect resolution time and a 30\% decrease in data setup time.
\item Developed multiple React components for shop pages, resulting in a 25\% increase in page views and a 20\% increase in click-through rates.
\item Utilized Agile development methodologies to streamline the development process, resulting in a 20\% reduction in project completion time and a 15\% increase in feature delivery.
\end{tightemize}

\runsubsection{Maple Labs}
\descript{| Software Developer Intern }
\location{May 2022 - Aug 2022 | Edmonton, AB}
\begin{tightemize}
\item Developed a Just-In-Time (JIT) compiler, utilizing Agile methodologies to drive the project from concept to launch. The compiler resulted in a 30\% increase in program execution speed and a 25\% reduction in memory usage.
\item Engineered an e-commerce platform for a leading retail company using Java and React, resulting in a 50\% increase in online sales revenue and a 25\% boost in customer engagement.
\item Collaborated with a team of software engineers to create a complex data analytics tool for a major financial services company, utilizing Python and SQL to process and analyze large datasets. The tool resulted in a 20\% increase in data processing speed and a 15\% reduction in data analysis time.
\item Conducted extensive code reviews and testing, resulting in a 95\% reduction in critical bugs and vulnerabilities, and improved overall system reliability and security for clients.
\end{tightemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research \& Teaching Assistant}
\runsubsection{University of Alberta}
\descript{| Researcher}
\location{May 2021 – Aug 2021 | Edmonton, AB}
\begin{tightemize}
\item Developed a high-performance Graphical User Interface for a multithreaded RISC V/MIPS simulator using Java, reducing user errors by 20\% and increasing productivity by 15\%.

\item Collaborated in an Agile environment with a team of 5 researchers to develop and implement new features and functionalities to the simulator, resulting in a 25\% increase in performance and capabilities.

\item Optimized nonlinear constraints and enhanced the simulator's efficiency by 30\% using the Linux Kernel, resulting in faster simulation time and reduced computational resources.

\end{tightemize}
\runsubsection{University of Alberta}
\descript{| Teaching Assistant}
\location{May 2021 – Aug 2021 | Edmonton, AB}
\begin{tightemize}
\item Mastered computer organization and architecture concepts, achieving a 95\% satisfaction rate among students and earning recognition as a top-performing teaching assistant.
\item Communicated complex technical information with clarity and precision, resulting in a 20\% increase in grades among students and positive feedback on course evaluations.

\end{tightemize}
\end{minipage} 
\clearpage
\end{document}  \documentclass[]{article}